Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-22 co-regular-EPQ.tex
sec 4.1.1.

%TODO WHY IT IS A SET OF AUTOMATA ? SAY WHAT ARE THE CASES THAT NEED TO BE COVERED. SAY WHAT IS THE CASE WE GIVE IN THE FIGURE. USE $\top$ AS MENTIONED AT THE BEGINNING OF THE SECTION INSTEAD OF 	$c$. USE BIG CAPS FOR SETS OF TRANSITION LABELS.
TODO COMPLETE THE FOLLOWING
Defining a $\mathsf{MatchedMaxPriority}^>$-complete automaton needs to consider ?? cases depending on the order between ??. For each case, we define an automaton recognizing the induced set of violations. For example, the automaton corresponding to the case ?? is pictured in in \figurename~\ref{fig:automata APQ1Lar-1 in paper}. More details can be found in Appendix \ref{sec:appendix proof and definition in section co-regular of EPQ1Lar}.

{\color {blue} 
Defining a $\mathsf{MatchedMaxPriority}^>$-complete automaton needs to capture the executions when a value $x$ is covered by values with smaller priority. By data-independence, we rename $x$ into $b$, rename the items covers it into $a$ and rename all other value into $\top$. There are four possibility of projection of captured execution into $b$, and for clarity we construct a register automaton for each of these case. For example, one such case is as in \figurename~\ref{fig:introduce gap for EPQ1Lar} (consider $b$ as $x$), and the corresponding register automaton is shown in \figurename~\ref{fig:automata APQ1Lar-1 in paper}. There are three possible place of the first $\textit{call}(\textit{put},a,\_)$ in the captured execution, as shown in \figurename~\ref{fig:executions APQ1Lar-1 in paper}. These three possible places correspond to three paths in $\mathcal{A}_{\textit{l-lar}}^1$: $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_7$, $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_{10}$ and $q_1 \rightarrow q_9 \rightarrow q_{10} \ldots \rightarrow q_7$. More details can be found in Appendix \ref{sec:appendix proof and definition in section co-regular of EPQ1Lar}. 
}

>>>>

%TODO WHY IT IS A SET OF AUTOMATA ? SAY WHAT ARE THE CASES THAT NEED TO BE COVERED. SAY WHAT IS THE CASE WE GIVE IN THE FIGURE. USE $\top$ AS MENTIONED AT THE BEGINNING OF THE SECTION INSTEAD OF 	$c$. USE BIG CAPS FOR SETS OF TRANSITION LABELS.
To define a $\mathsf{MatchedMaxPriority}^>$-complete automaton we need to consider several cases depending on the order between the call/return actions of the $\textit{put}$/$\textit{rm}$ operations that add and respectively, remove the value $b$. For example, the case where the put happens-before the remove (as in \figurename~\ref{fig:introduce gap for EPQ1Lar}) is pictured in \figurename~\ref{fig:automata APQ1Lar-1 in paper}. This automaton captures the three possible ways of ordering the first action $\textit{ret}(\textit{put},a,\_)$ w.r.t. the actions with value $b$, which are pictured in \figurename~\ref{fig:executions APQ1Lar-1 in paper} (this action cannot occur after $\textit{call}(\textit{rm},b,\_)$ since $b$ must be covered by the $a$s). The paths corresponding to these three possible orders are: $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_7$, $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_{10}$ and $q_1 \rightarrow q_9 \rightarrow q_{10} \ldots \rightarrow q_7$. Automata for the other cases can be found in Appendix \ref{sec:appendix proof and definition in section co-regular of EPQ1Lar}.

%For each case, we define an automaton recognizing the induced set of violations. 
%For example, the automaton corresponding to the case ?? is pictured in in \figurename~\ref{fig:automata APQ1Lar-1 in paper}. More details can be found in Appendix \ref{sec:appendix proof and definition in section co-regular of EPQ1Lar}.
%
%
%{\color {blue} 
%Defining a $\mathsf{MatchedMaxPriority}^>$-complete automaton needs to capture the executions when a value $x$ is covered by values with smaller priority. By data-independence, we rename $x$ into $b$, rename the items covers it into $a$ and rename all other value into $\top$. There are four possibility of projection of captured execution into $b$, and for clarity we construct a register automaton for each of these case. For example, one such case is as in \figurename~\ref{fig:introduce gap for EPQ1Lar} (consider $b$ as $x$), and the corresponding register automaton is shown in \figurename~\ref{fig:automata APQ1Lar-1 in paper}. There are three possible place of the first $\textit{call}(\textit{put},a,\_)$ in the captured execution, as shown in \figurename~\ref{fig:executions APQ1Lar-1 in paper}. These three possible places correspond to three paths in $\mathcal{A}_{\textit{l-lar}}^1$: $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_7$, $q_1 \rightarrow q_2 \rightarrow q_3 \ldots \rightarrow q_{10}$ and $q_1 \rightarrow q_9 \rightarrow q_{10} \ldots \rightarrow q_7$. More details can be found in Appendix \ref{sec:appendix proof and definition in section co-regular of EPQ1Lar}. 
%}
